Data Management \\ and LSST Special Programs

### 2022-02-21 DMTN-065.tex
fix reqparam refs

As a side note, no User-Generated pipeline may contribute Alerts to the LSST Alert Stream, and since the latency on image availability is ``within 24 hours" (\reqparam{L1PublicT}) no User-Generated pipeline would be able to obtain and process Special Programs data on a timescale similar to the Alert Stream (60 seconds, \reqparam{OTT1}).

>>>>

As a side note, no User-Generated pipeline may contribute Alerts to the LSST Alert Stream, and since the latency on image availability is ``within 24 hours" ({\tt L1PublicT}\reqparam{L1PublicT}) no User-Generated pipeline would be able to obtain and process Special Programs data on a timescale similar to the Alert Stream (60 seconds, {\tt OTT1}\reqparam{OTT1}).

### 2022-02-21 ap_docrev.tex
renamed ap prev proc sp
spcs
fix lse
fix reqparam refs

\section{Rubin Documentation Review}\label{sec:docrev}

@@

In Section 2.4.1.1.2, ``Non-Standard Visit", LSR-REQ-0111\req{0111} requires that the LSST system {\it ``be capable of obtaining and processing exposures not taken in a standard visit mode including those with a minimum exposure time of"} 1 second (\reqparam{minExpTime}).
The discussion notes that {\it ``non-standard visit exposures may possibly be degraded in some aspects of performance (e.g. cosmic ray rejection on visits consisting of a single exposure), and might be incompatible with difference imaging and alert production (e.g., short exposures in which the PSF is
not fully formed)"}.

@@

In Section 2.7.1.6, ``Community Computing Services", LSR-REQ-0055\lsrreq{0055} requires that the LSST system {\it ``shall provide and maintain an amount of computing capacity equivalent to at least"} 10\% (\reqparam{userComputingFraction}) {\it ``of the total LSST data processing capacity (computing and storage) for the purpose of scientific analysis of LSST data and the production of"} User-Generated data products. 
The discussion clarifies that the scope of this service remains to be determined.
This level of computational resources includes user processing of Special Programs data.

@@

In Section 3.6.1.4, ``Minimum Exposure Time", OSS-REQ-0291\ossreq{0291} specifies that {\it ``the camera shall be able to obtain a single exposure with an effective minimum exposure time of no more than"} 1 second (\reqparam{minExpTime}) {\it ``with a goal of an effective minimum exposure time of"} 0.1 seconds (\reqparam{minExpTimeGoal}). 
The discussion clarifies that {\it ``if the exposure is shortened from the 15 second nominal, the spacing between successive exposures should be extended to maintain the average readout rate consistent with a 15 second exposure"}, which may increase the overheads of Special Programs using short exposure times.
The discussion also clarifies that {\it ``if the exposure is lengthened from the 15 second nominal, the thermal stability may be affected, which may affect photometric accuracy"}.

@@

In Section 3.6.2.1.2, ``Maximum time for operational filter change", OSS-REQ-0293\ossreq{0293} specifies that {\it ``the camera system shall provide the capability of changing the operational filter with any other internal filter in a time less than"} 120 seconds (\reqparam{tFilterChange}).
This would impose a large overhead on, e.g., a Special Program that changes filters often without slewing.
See also OSS-REQ-0295\ossreq{0295}, Appendix~\ref{sec:hardbounds} of this document, and/or the filter change memorandum (\url{ls.st/spt-494}), for more information about the total lifetime number of filter changes.

In Section 3.6.3.3, ``Rotator tracking Time, OSS-REQ-0301\ossreq{0301} specifies that {\it ``the LSST shall be able to maintain field rotation tracking over a period of at least"} 1 hour (\reqparam{rotTrackTime}).
The discussion clarifies that this {\it ``is driven by the need to conduct extended 'deep drilling' observations on a single field}.
There do not seem to be any constraints on the speed of the rotator or the minimum distance between successive visits.

In Section 3.6.3.10, ``Non-Sidereal Tracking", OSS-REQ-0380\ossreq{0380} specifies that {\it ``the LSST system shall be capable of tracking in an arbitrary direction on the sky along a parametric RA(t) and DEC(t) trajectory, at angular rates of up to"} 220 arcseconds per second (\reqparam{nonsiderealAngularRateEl} and \reqparam{nonsiderealAngularRateAZ}) {\it ``with a tracking error not to exceed"} 0.5 arcseconds per minute (\reqparam{nonsiderealTrackingError}).
The discussion notes that {\it ``this is standard capability for modern telescopes"}, but might be relevant to some Special Programs.

@@

In Section 1.6.4, ``Constraints on Level 1 Special Program Products Generation", DMS-REQ-0344\dmreq{0344} specifies that {\it ``the publishing of [Prompt] data products from Special Programs shall be subject to the same performance requirements of"} 24 hours (\reqparam{L1PublicT}) for the release of Prompt data products and 1 minute (\reqparam{OTT1}) for the transmission of Alert packets.
This is essentially a more detailed version of DMS-REQ-0321 which includes the Alert production timescale.
This requirement is also derived from OSS-REQ-0392, which is essentially a flow-down of requirents from the LSR (0122, 0075, and 0121).

@@

Version 3.6 (revision 2021-12-17), \citeds{LSE-163}.

>>>>

\section{Documentation Review for Requirements Related to Special Programs}\label{sec:docrev}

@@

In Section 2.4.1.1.2, ``Non-Standard Visit", LSR-REQ-0111\req{0111} requires that the LSST system {\it ``be capable of obtaining and processing exposures not taken in a standard visit mode including those with a minimum exposure time of"} 1 second ({\tt minExpTime}\reqparam{minExpTime}).
The discussion notes that {\it ``non-standard visit exposures may possibly be degraded in some aspects of performance (e.g. cosmic ray rejection on visits consisting of a single exposure), and might be incompatible with difference imaging and alert production (e.g., short exposures in which the PSF is
not fully formed)"}.

@@

In Section 2.7.1.6, ``Community Computing Services", LSR-REQ-0055\lsrreq{0055} requires that the LSST system {\it ``shall provide and maintain an amount of computing capacity equivalent to at least"} 10\% ({\tt userComputingFraction}\reqparam{userComputingFraction}) {\it ``of the total LSST data processing capacity (computing and storage) for the purpose of scientific analysis of LSST data and the production of"} User-Generated data products. 
The discussion clarifies that the scope of this service remains to be determined.
This level of computational resources includes user processing of Special Programs data.

@@

In Section 3.6.1.4, ``Minimum Exposure Time", OSS-REQ-0291\ossreq{0291} specifies that {\it ``the camera shall be able to obtain a single exposure with an effective minimum exposure time of no more than"} 1 second ({\tt minExpTime}\reqparam{minExpTime}) {\it ``with a goal of an effective minimum exposure time of"} 0.1 seconds ({\tt minExpTimeGoal}\reqparam{minExpTimeGoal}). 
The discussion clarifies that {\it ``if the exposure is shortened from the 15 second nominal, the spacing between successive exposures should be extended to maintain the average readout rate consistent with a 15 second exposure"}, which may increase the overheads of Special Programs using short exposure times.
The discussion also clarifies that {\it ``if the exposure is lengthened from the 15 second nominal, the thermal stability may be affected, which may affect photometric accuracy"}.

@@

In Section 3.6.2.1.2, ``Maximum time for operational filter change", OSS-REQ-0293\ossreq{0293} specifies that {\it ``the camera system shall provide the capability of changing the operational filter with any other internal filter in a time less than"} 120 seconds ({\tt tFilterChange}\reqparam{tFilterChange}).
This would impose a large overhead on, e.g., a Special Program that changes filters often without slewing.
See also OSS-REQ-0295\ossreq{0295}, Appendix~\ref{sec:hardbounds} of this document, and/or the filter change memorandum (\url{ls.st/spt-494}), for more information about the total lifetime number of filter changes.

In Section 3.6.3.3, ``Rotator tracking Time, OSS-REQ-0301\ossreq{0301} specifies that {\it ``the LSST shall be able to maintain field rotation tracking over a period of at least"} 1 hour ({\tt rotTrackTime}\reqparam{rotTrackTime}).
The discussion clarifies that this {\it ``is driven by the need to conduct extended 'deep drilling' observations on a single field}.
There do not seem to be any constraints on the speed of the rotator or the minimum distance between successive visits.

In Section 3.6.3.10, ``Non-Sidereal Tracking", OSS-REQ-0380\ossreq{0380} specifies that {\it ``the LSST system shall be capable of tracking in an arbitrary direction on the sky along a parametric RA(t) and DEC(t) trajectory, at angular rates of up to"} 220 arcseconds per second ({\tt nonsiderealAngularRateEl}\reqparam{nonsiderealAngularRateEl} and {\tt nonsiderealAngularRateAZ}\reqparam{nonsiderealAngularRateAZ}) {\it ``with a tracking error not to exceed"} 0.5 arcseconds per minute ({\tt nonsiderealTrackingError}\reqparam{nonsiderealTrackingError}).
The discussion notes that {\it ``this is standard capability for modern telescopes"}, but might be relevant to some Special Programs.

@@

In Section 1.6.4, ``Constraints on Level 1 Special Program Products Generation", DMS-REQ-0344\dmreq{0344} specifies that {\it ``the publishing of [Prompt] data products from Special Programs shall be subject to the same performance requirements of"} 24 hours ({\tt L1PublicT}\reqparam{L1PublicT}) for the release of Prompt data products and 1 minute ({\tt OTT1}\reqparam{OTT1}) for the transmission of Alert packets.
This is essentially a more detailed version of DMS-REQ-0321 which includes the Alert production timescale.
This requirement is also derived from OSS-REQ-0392, which is essentially a flow-down of requirents from the LSR (0122, 0075, and 0121).

@@

Version 3.6 (revision 2021-12-17), \citeds{lse-163}.
